Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2017-06-26 paper/structureScene.tex
update link to github repo

The implementations of the presented methods and the experimental protocol are available online.\footnote{\url{https://github.com/mathieulagrange/taslp16}} % \ja{What is ``the one''?}

>>>>

The implementations of the presented methods and the experimental protocol are available online.\footnote{\url{https://github.com/mathieulagrange/tetci17}} % \ja{What is ``the one''?}
